### 2018-01-08 readme.rmd
reworded

- Both full matrices support Ctenophora-sister under the CAT-GTR+G model (Figure 3, right panel, left column, top two cells). 
- Most analyses under the CAT-GTR+G model do not provide significant support for either Ctenophora-sister or Porifera-sister (Figure 3, right panel, 10 blue cells)
- A subset of matrices with reduced species sampling and recoded data provide significant support for Porifera-sister (Figure 3, right panel, 4 green cells)

>>>>

- Both full matrices support Ctenophora-sister under the CAT-GTR+G model (Figure 3, right panel, left column, top two cells).
- Most analyses under the CAT-GTR+G model do not provide significant support for either Ctenophora-sister or Porifera-sister (Figure 3, right panel, 10 blue cells)
- A subset of matrices with recoded data, most of which also have reduced species sampling, provide significant support for Porifera-sister (Figure 3, right panel, 4 green cells)
